A 38 Million Year Old Mini-Neptune in the Kepler Field

### 2021-09-28 paper/ms.tex
update ms

% 208 words (250 max)
\begin{abstract}
  Kepler\,1627A is a G8V star previously known to host a
  $3.4\,R_\oplus$ mini-Neptune on a 7.2\,day orbit.  The star was
  observed by the Kepler space telescope because it is nearby
  ($d=329\pm3\,{\rm pc}$) and it resembles the Sun.  Here we show
  using Gaia kinematics, TESS stellar rotation periods, and
  spectroscopic lithium abundances that Kepler\,1627 is a member of
  the \clusterage\ old $\delta$~Lyr cluster.  To our knowledge,
  Kepler\,1627Ab is the youngest planet with a precise age yet found
  by the main Kepler mission.  The Kepler photometry shows two notable
  anomalies: the average Kepler transit profile appears to be
  asymmetric, and the individual transits show a correlation between
  the transit time and the local light curve slope.
  % The former could be explained by a dusty atmospheric outflow; the
  % latter could be explained by unresolved starspot crossings of a
  % planet on a prograde orbit.  
  We discuss plausible explanations for the light curve anomalies, and
  also highlight broader implications for our ability to expand the census
  of age-dated planets.
\end{abstract}

@@

In the context of the transiting planet population, \pn\ is among the
youngest known (Figure~\ref{fig:rp_period_age}).  Comparable systems
with precise ages include K2-33, DS~Tuc, HIP~67522,
TOI~837, the two-planet AU~Mic system, and the four-planet V1298~Tau
system
\citep{Mann_K2_33b_2016,David_et_al_2017,newton_tess_2019,david_four_2019,bouma_cluster_2020,plavchan_planet_2020,martioli_aumicbc_2021}.
\pn\ is one of the smallest planets in this sample ($3.4\pm
0.2\,R_\oplus$), which could be linked to the selection effects
imposed by the spot-induced photometric variability at very young ages
\citep[{\it e.g.},][]{zhou_2021_tois}.  Assuming that these young
planets have masses between $\approx$5$\,M_\oplus$ and 10$\,M_\oplus$,
their large sizes and presumed low densities would be in accord with
the expectation that mini-Neptunes start their lives with large
primordial atmospheres that are shed over the first gigayear
\citep{Owen_Wu_2013,Fulton_et_al_2017,ginzburg_corepowered_2018}.  The
prograde orbit, if confirmed, would be consistent with a quiescent
disk-driven migration history, and would differ from misalignments that
have been observed for some older
hot Neptunes~\citep{sanchis-ojeda_starspots_2011,albrecht_obliquities_2012,dalal_2019_hd3167,rubenzahl_tess-keck_2021}.
%Spectroscopic follow-up observations of the transit remain necessary
%however to verify whether the TTV-slope correlation is yielding the
%correct orbital geometry.

>>>>

% 208 words (250 max)
\begin{abstract}
  Kepler\,1627A is a G8V star previously known to host a
  $3.4\,R_\oplus$ mini-Neptune on a 7.2\,day orbit.  The star was
  observed by the Kepler space telescope because it is nearby
  ($d=329\,{\rm pc}$) and it resembles the Sun.  Here we show
  using Gaia kinematics, TESS stellar rotation periods, and
  spectroscopic lithium abundances that Kepler\,1627 is a member of
  the \clusterage\ old $\delta$~Lyr cluster.  To our knowledge, this makes
  Kepler\,1627Ab the youngest planet with a precise age yet found
  by the main Kepler mission.
  The Kepler photometry shows two 
  peculiarities: the average transit profile appears to be
  asymmetric, and the individual transit times are correlated with the local light curve slope.
  % The former could be explained by a dusty atmospheric outflow; the
  % latter could be explained by unresolved starspot crossings of a
  % planet on a prograde orbit.  
  We discuss possible explanations for these anomalies, and
  highlight broader implications for our ability to expand the census
  of age-dated planets.
\end{abstract}

@@

In the context of the transiting planet population, \pn\ is among the
youngest known (Figure~\ref{fig:rp_period_age}).  Comparable systems
with precise ages include K2-33
\citep{Mann_K2_33b_2016,David_et_al_2017}, DS~Tuc
\citep{benatti_possibly_2019,newton_tess_2019} , HIP~67522
\citep{rizzuto_tess_2020}, TOI~837
\citep{bouma_cluster_2020}, the two-planet AU~Mic system
\citep{plavchan_planet_2020,martioli_aumicbc_2021} and the four-planet
V1298~Tau system \citep{david_four_2019}.  \pn\ is one of the smallest
planets in this sample ($3.4\pm
0.2\,R_\oplus$), which could be linked to the selection effects
imposed by the spot-induced photometric variability at very young ages
\citep[{\it e.g.},][]{zhou_2021_tois}.  Assuming that these young
planets have masses between $\approx$5$\,M_\oplus$ and 10$\,M_\oplus$,
their large sizes and presumed low densities would be in accord with
the expectation that mini-Neptunes start their lives with large
primordial atmospheres that are shed over the first gigayear
\citep{Owen_Wu_2013,Fulton_et_al_2017,ginzburg_corepowered_2018}.  The
prograde orbit, if confirmed, would be consistent with a quiescent
disk-driven migration history, and would differ from misalignments that
have been observed for some older
hot Neptunes~\citep{sanchis-ojeda_starspots_2011,albrecht_obliquities_2012,dalal_2019_hd3167,rubenzahl_tess-keck_2021}.
%Spectroscopic follow-up observations of the transit remain necessary
%however to verify whether the TTV-slope correlation is yielding the
%correct orbital geometry.
